### 2014-04-14 paper.tex
Added additional work.

% rename this file to foo.tex and then compile using 
%
%  latex foo
%
% view it with 
%
%  xdvi foo
%
% In order to print, create a PostScript file with
%
%  dvips foo
%
% then use
%
%  lpr -Pps2 foo.ps
%
% Have fun!
%
% Andreas
%
\documentclass{article}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{wrapfig}
\usepackage[all]{xy}

@@

Eric Whitman looks into using Multiple Model Dynamic (MMD) Programming, and uses the inverted pendulum swing-up problem to demonstrate the algorithm.

 http://www.contrib.andrew.cmu.edu/~ewhitman/thesis.pdf

@@

Define the state space as $x={\theta, \omega}$, and the action space to be $u={\tau}$. We let pointing up, $\theta = 0$, as the pendulum to be pointing up, and we are optimizing the pendulum to reach $\theta = 0$, with zero velocity, $\omega = 0$, using the minimum torque necessary. We define the cost function be to $C$:

\begin{equation} 
C(x,u) = \omega^2 + 0.5 \cdot \omega^2 + \tau^2
\end{equation}

@@

\begin{equation} 
C = \int L(x,u) dt %TODO: WHERE DID L COME FROM?!
\end{equation}

@@

And if $V'(x)<C(x,u) + \omega V(x_{k+1}(U(x))), we let V'(x)$ and $U(x)={\tau'}$.

@@

\begin{equation} 
{x'}_1
\begin{bmatrix}
\frac{\pi}{2} + 0.003048645 \\
1.03243
\end{bmatrix}
\end{equation}

@@

Since 2.6032705 < 2.6062750, we learn that we are applying a torque in the wrong direction, and it is better to let gravity pull on the pendulum instead of applying addition torque, and keep the value, $U(x)={0}$. Now suppose we guess $\tau = -1$, we find that 
\begin{equation} 
{x'}_1
\begin{bmatrix}
\frac{\pi}{2} + 0.003039645 \\
1.02643
\end{bmatrix}
\end{equation}
With the value
\begin{equation} 
V'(x) = 2.6002660
\end{equation}

Since 2.6032705 > 2.6002660, we change the value $U(x_0)={-1}$. Giving a new optimal torque to apply at that point.

@@

Until 2001 developers could only use shaders that were pre-programmed into the hardware, and then Direct3D 8 (http://en.wikipedia.org/wiki/Direct3D) gave developers the option to program custom shaders that run in the hardware.

The main drive for GPU development was for computer graphics, but a technique known as fragment processing (?) was used to perform other types of computation. Fragment processing involves data processing and storage through image textures.

@@

http://www.mathematik.uni-dortmund.de/~goeddeke/gpgpu/tutorial.html

@@

\section{Full-body controller}
Intro...Carnegie Mellon University developed custom software for controlling the robot, which involves two major aspects that are solve using Quadratic programming, an Inverse Kinematics solver, and an Inverse Dynamics solver. 
\subsection{Inverse Kinematics}

@@

The gradratic programming is solved using a re-written version of QuadProg++[http://quadprog.sourceforge.net/], but adapted to use Eigen.

@@

\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx} 
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{wrapfig}
\usepackage[all]{xy}
\usepackage{cite}

@@

Eric Whitman looks into using Multiple Model Dynamic (MMD) Programming, and uses the inverted pendulum swing-up problem to demonstrate the algorithm. \cite{eric_thesis}

@@

Define the state space as $x=\{\theta, \omega\}$, and the action space to be $u=\{\tau\}$. We define the pendulum to be pointing up at, $\theta = 0$, and we are optimizing the pendulum to reach $\theta = 0$, with zero velocity, $\omega = 0$, using the minimum torque necessary. We define the cost function be to $L$:

\begin{equation} 
L(x,u) = \theta^2 + 0.5 \cdot \omega^2 + \tau^2
\end{equation}

@@

\begin{equation} 
C = \int L(x,u) dt
\end{equation}

@@

And if $V'(x)<C(x,u) + \gamma V(x_{k+1}(U(x)))$, we let $V'(x)$ and $U(x)={\tau'}$.

@@

\begin{equation} 
{x'}_1 = 
\begin{bmatrix}
\frac{\pi}{2} + 0.003048645 \\
1.03243
\end{bmatrix}
\end{equation}

@@

Since $2.6032705 < 2.6062750$, we learn that we are applying a torque in the wrong direction, and it is better to let gravity pull on the pendulum instead of applying addition torque, and keep the value, $U(x)={0}$. Now suppose we guess $\tau = -1$, we find that 
\begin{equation} 
{x'}_1 = 
\begin{bmatrix}
\frac{\pi}{2} + 0.003039645 \\
1.02643
\end{bmatrix}
\end{equation}
With the value
\begin{equation} 
V'(x) = 2.6002660
\end{equation}

Since $2.6032705 > 2.6002660$, we change the value $U(x_0)={-1}$. Giving a new optimal torque to apply at that point.

@@

Until 2001 developers could only use shaders that were pre-programmed into the hardware, and then Direct3D 8 \cite{wiki:direct3d} gave developers the option to program custom shaders that run in the hardware.

The main drive for GPU development was for computer graphics, but using some technique, one could speed up large linear algebra processing using storage through image textures. \cite{Goeddeke:2005:GBM}

@@

@@

\section{Full-body controller}
Intro...Carnegie Mellon University developed custom software for controlling the robot, which involves two major aspects that are solve using Quadratic programming, an Inverse Kinematics solver, and an Inverse Dynamics solver.

\subsection{Inverse Kinematics}
Inverse kinematics is the process of given an desired end effector position, generate a joint state that will as close as possible achieve the goal. There exists a great deal of research, and libraries that provide fast and concise solutions, but most of the research assumes that the base of the joint system does not move, such as one that you might find on a factory.

Atlas is a bipedal robot, it is not simple to define a set of rules that describes all possible motions.

We perform a trick, we define the robot as skeleton starting from the pelvis, but when we generate Jacobians to move the end effector of each limbs, we also give it the ability to move the pelvis on a global coordinate frame.

@@

The gradratic programming is solved using a re-written version of QuadProg++[http://quadprog.sourceforge.net/], but adapted to use Eigen. The algorithm implements the Goldfarb-Idnani active-set dual method. At present it is limited to the solution of strictly convex quadratic programs. \cite{quadprog}

@@

\bibliography{referencex}
\bibliographystyle{plain}
\end{document}
